MSD panels 1, 2 and 3 Explant Supernatant

### 2016-09-21 MSD_panels_1_2_3_explant_sup_analysis.Rmd
minor plot edits

---
title: "MSD panels 1, 2 and 3 Explant Supernatant"
output: html_document
---

@@

ggplot(mergeMock, aes(x = Timepoint, y = MockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  #geom_hline(yintercept = 0)+
  ggtitle("Analyte Concentrations by Donor, Timepoint and Condition")

@@

ggplot(subset, aes(x = Timepoint, y = MockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Analyte Concentrations by Donor, Timepoint and Condition")

>>>>

---
title: "MSD panels 1, 2 and 3 Explant Supernatant"
output: github_document
---

@@

ggplot(mergeMock, aes(x = Timepoint, y = MockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "log 10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  #geom_hline(yintercept = 0)+
  ggtitle("Analyte Concentrations")

@@

ggplot(subset, aes(x = Timepoint, y = MockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "log10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Analyte Concentrations")
